\begin{document}

% Name
\noindent {\huge Shaun Sequeira}

% Contact Information
\noindent\begin{tabularx}{\textwidth}{@{}XXX@{}}
\faPhone\enspace 437-971-7883 & \faEnvelopeO\enspace shaun.sequeira88@gmail.com & \faGlobe\enspace Portfolio \\
\faLinkedin\enspace linkedin.com/in/shaunsequeira08 & \faGithub\enspace github.com/knat01 & \\
\end{tabularx}

\vspace{2mm}

% Experience
\section{Experience}

\noindent{\bf Royal Bank of Canada} \hfill Toronto, ON\\
{\it Full Stack Developer} \hfill August 2022 – August 2023
\begin{itemize} \itemsep -1pt % Reduce space between items
    \item Led the development of an application, streamlining the data transfer process for RBC employees. Automated data transfer and permission handling, reducing file transfer time from one week to immediate action.
    \item Enabled instant file transfers to \textbf{AWS S3} and \textbf{Snowflake}, boosting productivity by allowing users to independently request access and transfer files.
    \item Designed and implemented a secure service layer using \textbf{Python} for managing user access requests and approvals, facilitating authorization of data movement to the cloud.
    \item Architected a comprehensive database schema in \textbf{PostgreSQL}, focusing on performance and scalability.
    \item Developed a web application using \textbf{React} and \textbf{TypeScript}, enabling 1000+ employees in the Tech\&Ops department to request data transfer permissions and send data directly to S3 buckets and Snowflake.
    \item Containerized the application using \textbf{Docker}, enhancing operational efficiency and streamlining deployment.
    \item Hands-on experience in setting up and managing multiple \textbf{CI/CD pipelines}, ensuring efficient and reliable software delivery to production environments.
    \item Employed \textbf{Grafana} for monitoring and visualization, aiding in performance optimization and health tracking.
\end{itemize}

% Education
\section{Education}

\noindent{\bf Toronto Metropolitan University} \hfill Toronto, ON\\
{\it Bachelor of Science in Computer Science} \hfill August 2019 – October 2024

% Projects
\section{Projects}

\noindent{\bf Financial Insights RAG} | \emph{Python, Streamlit, LangChain, LlamaIndex, OpenAI API, Alpha Vantage API}
\begin{itemize} \itemsep -1pt
    \item Developed an AI-powered financial insights web application leveraging Retrieval-Augmented Generation (RAG) to provide comprehensive analysis of publicly traded companies.
    \item Integrated real-time financial data from multiple APIs including Alpha Vantage, and more, allowing users to explore dynamic financial metrics.
    \item Implemented AI-driven insights using OpenAI API and LangChain, generating natural language summaries and responses for financial data and reports.
    \item Utilized LlamaIndex for document processing, enabling efficient indexing and retrieval of information from uploaded annual reports.
    \item Designed interactive data visualizations with Plotly, showcasing key financial trends.
    \item Implemented advanced NLP techniques to extract and summarize data from financial documents, making complex financial analysis accessible to users.
    \item Optimized the application for scalability and performance using cloud services, containerization, and efficient data processing pipelines.
\end{itemize}

\noindent{\bf Appl.ai} | \emph{Python, Selenium, OpenAI Assistants API, React}
\begin{itemize} \itemsep -1pt
    \item Developed Appl.ai, an advanced job search automation platform, employing Python for backend processing, integrating OpenAI Assistants API for NLP.
    \item Architected and implemented a dynamic resume and cover letter generation module using OpenAI Assistants API, customizing documents for individual user profiles and job descriptions.
    \item Designed and deployed a robust Selenium-based web scraper, capable of extracting data from online job boards.
    \item Developed a comprehensive resume parsing algorithm in Python, enabling intricate analysis of user resumes for effective job matching and optimization.
    \item Designed the front-end using React, focusing on intuitive navigation and responsive design.
\end{itemize}

% Technical Skills
\section{Technical Skills}

\begin{tabularx}{\textwidth}{@{}lX@{}}
\textbf{Languages:}       & Python, C++, C, JavaScript, TypeScript, SQL, HTML, CSS, PHP, MATLAB, Java \\
\textbf{Frameworks:}     & Node.js, Boto3, React, FastAPI, Flask, CodeLLama, LangChain, LlamaIndex, PyTorch, TensorFlow \\
\textbf{Infrastructure:} & Amazon S3, Kubernetes, Shopify, Postgres, MS Office, Wordpress, Docker, AWS Lambda, GCP, Azure \\
\textbf{Developer Tools:}& VS Code, Github, Visual Studio, Jupyter Notebooks, ChatGPT, Cursor IDE, Docker, Jenkins, Airflow \\
\end{tabularx}

% End the document
\end{document}