%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}



\begin{document}

\begin{center}
\headername{Shaun Sequeira}\\
\vspace{1mm}
♂phone437-971-7883 \hspace{1mm} /envelope\hspace{1mm}shaun.sequeira88@gmail.com \\
\hspace{1mm} /globe\hspace{1mm}Portfolio \hspace{1mm} /linkedin\hspace{1mm}linkedin.com/in/shaunsequeira08 \\
/github\hspace{1mm}github.com/knat01 \\
\end{center}

\begin{rSection}{Experience}

\begin{rSubsection}{Royal Bank of Canada}{August 2022 - August 2023}{Full Stack Developer}{Toronto, ON}
\item Led the development of an \textbf{application}, streamlining the data transfer process for RBC employees. \textbf{Automated data transfer} and permission handling, reducing file transfer time from one week to immediate action.
\item Enabled instant file transfers to \textbf{AWS S3} and \textbf{Snowflake}, boosting productivity by allowing users to independently request access and transfer files.
\item Designed and implemented a secure service layer using \textbf{Python} for managing user access requests and approvals, facilitating authorization of data movement to the cloud.
\item Architected a comprehensive database schema in \textbf{PostgreSQL}, focusing on performance and scalability.
\item Developed a web application using \textbf{React} and \textbf{TypeScript}, enabling 1000+ employees in the Tech\&Ops department to request data transfer permissions and send data directly to S3 buckets and Snowflake.
\item Containerized the application using \textbf{Docker}, enhancing operational efficiency and streamlining deployment.
\item Hands-on experience in setting up and managing multiple \textbf{CI/CD pipelines}, ensuring efficient and reliable software delivery to production environments.
\item Employed \textbf{Grafana} for monitoring and visualization, aiding in performance optimization and health tracking.
\end{rSubsection}

\end{rSection}

\begin{rSection}{Education}
\begin{rSubsection}{Toronto Metropolitan University}{August 2019 - October 2024}{Bachelor of Science in Computer Science}{Toronto, ON}
\end{rSubsection}
\end{rSection}

\begin{rSection}{Projects}

\begin{rSubsection}{Financial Insights RAG}{}
\item Developed an AI-powered \textbf{financial insights web application} leveraging \textbf{Retrieval-Augmented Generation (RAG)} to provide comprehensive analysis of publicly traded companies, integrating real-time data with AI-generated insights.
\item Integrated real-time financial data from multiple APIs including \textbf{Alpha Vantage}, Tiingo, World Trading Data, Twelve Data, Yahoo Finance, and more, allowing users to explore dynamic financial metrics.
\item Implemented AI-driven insights using \textbf{OpenAI API} and LangChain, generating natural language summaries and responses for financial data and reports.
\item Utilized LlamaIndex for document processing, enabling efficient indexing and retrieval of information from uploaded annual reports, providing users with fast and relevant financial data extraction.
\item Designed interactive data visualizations with Plotly, showcasing key financial trends such as profitability, liquidity, efficiency ratios, and stock performance over time.
\item Implemented advanced \textbf{Natural Language Processing (NLP)} techniques to extract and summarize data from financial documents, making complex financial analysis accessible to users.
\end{rSubsection}

\begin{rSubsection}{Appl.ai}{}
\item Developed Appl.ai, an advanced job search automation platform, employing \textbf{Python} for highly scalable and efficient backend processing, seamlessly integrating \textbf{OpenAI Assistants API} for cutting-edge natural language processing.
\item Architected and implemented a dynamic resume and cover letter generation module using \textbf{OpenAI Assistants API}, customizing documents to be \textbf{ATS-friendly} and uniquely tailored to individual user profiles and job descriptions.
\end{rSubsection}

\end{rSection}

\begin{rSection}{Technical Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Languages & Python, C++, C, JavaScript, TypeScript, SQL, HTML, CSS, PHP, MATLAB, Java \\
Frameworks & Node.js, Boto3, React, FastAPI, Flask, CodeLLama, LangChain, LlamaIndex, PyTorch, TensorFlow \\
Infrastructure & Amazon S3, Kubernetes, Shopify, Postgres, MS Office, Wordpress, Docker, AWS Lambda, GCP, Azure \\
Developer Tools & VS Code, Github, Visual Studio, Jupyter Notebooks, ChatGPT, Cursor IDE, Docker, Jenkins, Airflow \\
\end{tabular}

\end{rSection}

\end{document}
%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{center}
    {\Huge \scshape First Last} \\ \vspace{1pt}
    123 Street Name, Town, State 12345 \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ 123-456-7890 ~ \href{mailto:x@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{email@gmail.com}} ~ 
    \href{https://linkedin.com/in//}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/username}}  ~
    \href{https://github.com/}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/username}}
    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {State University}{Sep. 2017 -- May 2021}
      {Bachelor of Science in Computer Science}{City, State}
  \resumeSubHeadingListEnd

%------RELEVANT COURSEWORK-------
\section{Relevant Coursework}
    %\resumeSubHeadingListStart
        \begin{multicols}{4}
            \begin{itemize}[itemsep=-5pt, parsep=3pt]
                \item\small Data Structures
                \item Software Methodology
                \item Algorithms Analysis
                \item Database Management
                \item Artificial Intelligence
                \item Internet Technology
                \item Systems Programming
                \item Computer Architecture
            \end{itemize}
        \end{multicols}
        \vspace*{2.0\multicolsep}
    %\resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Electronics Company}{May 2020 -- August 2020}
      {Software Engineer Intern}{City, State}
      \resumeItemListStart
        \resumeItem{Developed a service to automatically perform a set of unit tests daily on a product in development in order to decrease time needed for team members to identify and fix bugs/issues.}
        \resumeItem{Incorporated scripts using Python and PowerShell to aggregate XML test results into an organized format and to load the latest build code onto the hardware, so that daily testing can be performed.}
        \resumeItem{Utilized Jenkins to provide a continuous integration service in order to automate the entire process of loading the latest build code and test files, running the tests, and generating a report of the results once per day.}
        \resumeItem{Explored ways to visualize and send a daily report of test results to team members  using HTML, Javascript, and CSS.}
      \resumeItemListEnd

    \resumeSubheading
      {Startup, Inc}{May 2019 -- August 2019}
      {Front End Developer Intern}{City, State}
      \resumeItemListStart
        \resumeItem{Assisted in development of the front end of a mobile application for iOS/Android using Dart and the Flutter framework.}
        \resumeItem{Worked with Google Firebase to manage user inputted data across multiple platforms including web and mobile apps.}
        \resumeItem{Collaborated with team members using version control systems such as Git to organize modifications and assign tasks.}
        \resumeItem{Utilized Android Studio as a development environment in order to visualize the application in both iOS and Android.}
    \resumeItemListEnd
    
  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Gym Reservation Bot} $|$ \emph{Python, Selenium, Google Cloud Console}}{January 2021}
          \resumeItemListStart
            \resumeItem{Developed an automatic bot using Python and Google Cloud Console to register myself for a timeslot at my school gym.}
            \resumeItem{Implemented Selenium to create an instance of Chrome in order to interact with the correct elements of the web page.}
            \resumeItem{Created a Linux virtual machine to run on Google Cloud so that the program is able to run everyday from the cloud.}
            \resumeItem{Used Cron to schedule the program to execute automatically at 11 AM every morning so a reservation is made for me.}
          \resumeItemListEnd
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{Ticket Price Calculator App} $|$ \emph{Java, Android Studio}}{November 2020}
          \resumeItemListStart
            \resumeItem{Created an Android application using Java and Android Studio to calculate ticket prices for trips to museums in NYC.}
            \resumeItem{Processed user inputted information in the back-end of the app to return a subtotal price based on the tickets selected.}
            \resumeItem{Utilized the layout editor to create a UI for the application in order to allow different scenes to interact with each other.}
          \resumeItemListEnd 
          \vspace{-13pt}
          \resumeProjectHeading
          {\textbf{Transaction Management GUI} $|$ \emph{Java, Eclipse, JavaFX}}{October 2020}
          \resumeItemListStart
            \resumeItem{Designed a sample banking transaction system using Java to simulate the common functions of using a bank account.}
            \resumeItem{Used JavaFX to create a GUI that supports actions such as creating an account, deposit, withdraw, list all acounts, etc.}
            \resumeItem{Implemented object-oriented programming practices such as inheritance to create different account types and databases.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-15pt}


%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, Java, C, HTML/CSS, JavaScript, SQL} \\
     \textbf{Developer Tools}{: VS Code, Eclipse, Google Cloud Platform, Android Studio} \\
     \textbf{Technologies/Frameworks}{: Linux, Jenkins, GitHub, JUnit, WordPress} \\
    }}
 \end{itemize}
 \vspace{-16pt}


%-----------INVOLVEMENT---------------
\section{Leadership / Extracurricular}
    \resumeSubHeadingListStart
        \resumeSubheading{Fraternity}{Spring 2020 -- Present}{President}{University Name}
            \resumeItemListStart
                \resumeItem{Achieved a 4 star fraternity ranking by the Office of Fraternity and Sorority Affairs (highest possible ranking).}
                \resumeItem{Managed executive board of 5 members and ran weekly meetings to oversee progress in essential parts of the chapter.}
                \resumeItem{Led chapter of 30+ members to work towards goals that improve and promote community service, academics, and unity.}
            \resumeItemListEnd
        
    \resumeSubHeadingListEnd


\end{document}
